Commutativity of operation-based CRDTs \\ CIS 673 Project Report

### 2020-04-18 report/draft.tex
Change a capital letter citation

Servois \cite{Bansal2018Servois} is a tool that automatically computes the
commutativity (and non-commutativity) conditions of abstract data types (ADTs). Unlike
previous tools that relied on random sampling or blackbox testing, Servois is
able to generate conservative approximations of commutativity conditions that
are guaranteed to be sound, even if they are partial. Servois is
\textit{relatively complete}: if it terminates, the commutativity conditions are
guaranteed to be complete but termination is not guaranteed.

>>>>

Servois \cite{bansal2018servois} is a tool that automatically computes the
commutativity (and non-commutativity) conditions of abstract data types (ADTs). Unlike
previous tools that relied on random sampling or blackbox testing, Servois is
able to generate conservative approximations of commutativity conditions that
are guaranteed to be sound, even if they are partial. Servois is
\textit{relatively complete}: if it terminates, the commutativity conditions are
guaranteed to be complete but termination is not guaranteed.
